Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-11-29 paper/referee_responses.md

> # Report of Referee A -- LD17005/Laeven
> The manuscript discusses numerical calculations related to how to improve the energy gap in 2D planar Josephson junctions.
> The manuscript considers 2D SNS junctions within clean-limit BdG tight-binding model, used also in previous studies of the same system. Specific N region geometry is considered, and found to improve the energy gap. The argument why this occurs appears clear, and the results valid. Improving energy gaps likely is useful, but it's less clear this is the main/only problem faced in the experiments.
> The effect of long trajectories in ballistic systems is itself not surprising or new, but optimizing the geometry for this in the specific context of Majorana realizations with planar SNS was apparently not considered before. The closer study of this is the main new contribution here.

We thank the referee for the positive evaluation, however, we would like to emphasize that geometry optimization was not considered as a method of gap engineering in Josephson junctions in any context, not just in the Majorana devices.

> However, the manuscript appears better suited for publication in PRB. Although optimizing parameters in a previously discussed model is interesting and probably useful for future experiments of this type, it does not appear a significant advance of wide interest to a broad audience.

Our work reports an idea of adjusting the geometry as a way of influencing a phenomenon that is known for decades.
That this was overlooked for so long, in a very mature field, is in our opinion what makes it exciting and interesting.
Further, we predict a change in the device properties by more than an order of magnitude.
This is a substantial advancement in the field of Majorana devices and therefore, makes our work satisfy the PRL criterion of importance.

> # Report of Referee B -- LD17005/Laeven
> The authors consider a planar Josephson junction in a zigzag geometry and propose it as an improved realization of a one-dimensional topological superconductor. As they show using numerical simulations, the zigzag geometry increases the induced superconducting gap and thereby decreases the spatial size of the Majorana wave functions, making them more protected.
> To the best of my knowledge the idea presented in the paper is novel. In my opinion, this work will influence future experiments, and can help solve the problem of a small topological gap in the planar Josephson junction. Moreover, the paper is well written. Assuming the authors can address the questions and comments listed below, I therefore recommend the publication of the paper in Physical Review Letters.

We thank the referee for the positive assessment of our work.

> My biggest concern has to do with the direction of the magnetic field as it is given in Eq. (1). The magnetic field considered in Eq. (1) does not penetrate the superconductor which is certainly reasonable. I think, however, that this is not consistent with the uniformly-directed magnetic field in the normal region (see B\sigma_x in Eq. (1a)). I would expect that in the zigzag geometry the magnetic field lines would be forced to curve in a zigzag manner to avoid approaching the superconductors in a direct angle. In this case, the direction of the Zeeman term in Eq. (1a) would depend on space. Can the authors give a compelling argument for why this would not affect the main results (or alternatively simulate a spatially-dependent magnetic field)?

We have performed a systematic investigation of the influence of the magnetic field direction on the device properties.
Because all the quasiparticle states are strongly coupled to the superconductor in the zigzag geometry, we observe that the magnetic field does not need to be aligned with the junction direction nearly as precisely as in a straight junction.
Specifically, we observe that even a 10-degree misalignment yields an induced gap of an order of magnitude larger than the gap in a straight junction with a perfectly aligned field.
We have also verified that a position-dependent magnetic field does not degrade the device performance.
We have reported these results these findings in the main text and added the detailed information in the appendix.
We thank the referee for the suggestion to investigate this phenomenon.

@@

> At the end of section III, the authors explain that besides the effect of increasing the gap through eliminating modes traveling at grazing angles, the zigzag geometry has two more effects that causes the Majorana size to decrease: (1) reducing the Fermi velocity, and (2) increasing transmission to the SC. With regards to (1), I would comment that the Fermi velocity that enters the formula \xi=v_F/E_gap is the electron velocity before introducing superconductivity. The fact that the bandstructure becomes flatter is not a testament to the Fermi velocity becoming smaller since superconductivity is already present. With regards to (2), it seems to me that this is exactly the original effect that increases the gap, and should not be counted as a separate effect. Indeed, the transmission of electrons traveling at grazing angles is originally very small (it’s not zero though due to the uncertainty principle), and it becomes bigger since the incident angle is now more direct.

After the Eq. (2), we have added a remark that this equation follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
This relation does not assume anything about the nature of v_F or E_gap.

In order to distinguish the effect of the increased interface transparency from the effect of removing long trajectories, we have performed an additional simulation of a device with the same angle of the zigzag boundaries, but a much smaller amplitude of the modulation.
While we do observe a gap enhancement in this device, consistent with the mechanism (2) mentioned by the referee, this enhancement is much smaller than in the device with a large modulation.
Therefore, we conclude that the two mechanisms are independent, however, the removal of the long trajectories is the dominant mechanism for the gap enhancement.
We have added the details of the additional simulation to the supplementary information.

@@

> Some smaller issues:
> Can the authors clarify the following statement from the introduction: “However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities”.

We thank the referee for pointing us to this vague sentence.
We have changed it to "However, tuning the system to a low chemical potential requires precise knowledge of the band positions and makes the device more sensitive to disorder or microscopic inhomogeneities."

> In the Discussion section, the authors mention that interface disorder can still cause a soft gap. Wasn’t that simulated in Fig. (3d)? A similar statement is made about a multimode junction. Does this refer to transverse modes in the z direction (perpendicular to the 2DEG)? because the system considered in the paper is indeed a multimode junction (due to the finite size in the y direction - W). Perhaps I didn’t understand the idea of the paragraph.

The reference 28 considers a variation in the coupling strength between a semiconductor and a superconductor that has a correlation length longer than the induced coherence length.
This scenario is therefore, very different from the short length scale roughness that we considered in Fig. 3(d).
Reference 30 describes a multimode mechanism and is about how the conductance looks rather than about the actual gap.

### 2020-01-06 paper/zigzag.tex
rewrite the conclusions

\comment{The gap is small because of long trajectories.}
An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
In clean systems a soft gap arises due to the reduction of the induced gap for states with the momentum directed along the junction~\cite{Gennes1963,Beenakker2005}.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_\textrm{F}$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length and $v_\textrm{F}$ the Fermi velocity.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005,Nijholt2016}.
However, tuning the system to a low chemical potential requires a precise knowledge of the band positions and makes the device more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2019} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Band structures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
The blue lines correspond to a trivial phase ($\phi=0$, $B_x = 0$) and the orange lines to a topological phase ($\phi=\pi$, $B_x = \SI{1}{T}$).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
Subplot (a) has a different $x$-scale for $k_x < 0$ from the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana size because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
\end{figure}

@@

\comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
In the unfolded band structure of a straight system, shown in Fig.~\ref{fig:band_structures}(a), the lowest energy states occur at $k \approx k_F$.
We interpret the increase of the gap $E_\textrm{gap}$ shown in Fig.~\ref{fig:band_structures}(b) and (c) as an effect of the zigzag geometry removing these long trajectories traveling at grazing angles.
Besides the increased $E_\textrm{gap}$, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
Finally, in a zigzag geometry, every trajectory encounters a superconductor close to normal incidence.
Normal incidence has a higher transmission probability for entering the superconductor and therefore a higher Andreev reflection amplitude.
This provides another mechanism of the gap enhancement.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for different geometries.
With (a) a straight system, (b) a zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for the straight system is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for the zigzag systems.
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
\end{figure}

@@

\comment{In a straight system, the Majoranas are very poorly localized because of small gap and high velocity}
We show the resulting Majorana wave function densities $\left| \psi_\textrm{M} \right|^2$ in different geometries in Fig.~\ref{fig:wave_functions} using the same Hamiltonian parameter values.
In the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
The small topological gap combined with the high velocity result in a large Majorana size
\begin{equation}
\label{eq:xi_M}
\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{E_\textrm{gap}}.
\end{equation}
This result follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
Therefore, in straight junctions the wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
We observe that in zigzag systems the Majorana properties improve independent of specific geometric details.
All of the zigzag-type geometries have $\xi_\textrm{M}$ improved by a factor $\sim 70$ and have the Majorana wave function localized within one segment of the zigzag.
Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher than in the straight junction, and as mentioned in section \ref{sec:band_structures}, the velocity $v_\textrm{F}$ is more than an order of magnitude lower.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/phasediagrams}
\caption{A comparison of a straight device (left panels) and a zigzag one (right panels).
The top panels show the Majorana wave functions, near the left edge of the system, at the value of $B_x$ for which $E_\textrm{gap}$ is maximized in a straight geometry for $\mu=\SI{10}{\meV}$ and $\phi=\pi$ as well as the values of the gap and the Majorana size.
The other panels show gap as a function of $\mu$ and $B_x$ at $\phi=\pi$ (middle panels) and as a function of $\phi$ and $B_x$ at $\mu=\SI{10}{\meV}$ (bottom panels).
The dashed lines and the dot indicate the parameters used in the other panels.
Additionally, in subplot (c) we overlay the phase boundaries.
The remaining parameter values are written at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
\label{fig:phasediagrams}}
\end{figure}

@@

\comment{The zigzag geometry is a controllable tool in hardening the gap and decreasing Majorana size.}
The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reduces Majorana size.
The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
The zigzag geometry offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, that otherwise has a similar effect.

\comment{Zigzag doesn't do anything against other mechanisms, and therefore it doesn't help to use it ignorantly}
Soft gap may arise due to other mechanisms that do not involve ballistic trajectories: both interface disorder and pair breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
Further in a multimode junction the mode dependence of transmission~\cite{Stanescu2014} may produce subgap conductance similar to that in a device with a soft gap.
The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool in distinguishing different mechanisms.

\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{Vries}.
We have demonstrated that the unavoidable variation in the experimental device geometry should not have a detrimental impact on the zigzag devices.

\comment{Optimizing the geometry, more detailed modeling, and a simple analytical estimation are open questions for further research}
Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a much harder question of finding the optimal geometry.
A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices.
Finally, we have neglected several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
While we expect these phenomena not to influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.

@@

\comment{In a realistic device the magnetic field might not be inhomogeneous, but zigzag doesn't care.}
The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.

>>>>

\comment{The gap is small because of long trajectories.}
An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
In clean systems a soft gap arises due to the reduction of the induced gap for states with the momentum directed along the junction~\cite{Gennes1963,Beenakker2005}.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_\textrm{F}$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length and $v_\textrm{F}$ the electron Fermi velocity.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005,Nijholt2016}.
However, tuning the system to a low chemical potential requires a precise knowledge of the band positions and makes the device more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2019} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Band structures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
The blue lines correspond to a trivial phase ($\phi=0$, $B_x = 0$) and the orange lines to a topological phase ($\phi=\pi$, $B_x = \SI{1}{T}$).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
Subplot (a) has a different $x$-scale for $k_x < 0$ from the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
Once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, the quasiparticle velocity $v$ decreases.
When the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana size $\xi_\textrm{M} \propto v/E_\textrm{gap}$.
The parameter values are listed at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
\end{figure}

@@

\comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
In the unfolded band structure of a straight system, shown in Fig.~\ref{fig:band_structures}(a), the lowest energy states occur at $k \approx k_F$.
We interpret the increase of the gap $E_\textrm{gap}$ shown in Fig.~\ref{fig:band_structures}(b) and (c) as an effect of the zigzag geometry removing these long trajectories traveling at grazing angles.
Besides the increased $E_\textrm{gap}$, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing quasiparticle velocity $v$.
This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
Finally, in a zigzag geometry, every trajectory encounters a superconductor close to normal incidence.
Normal incidence has a higher transmission probability for entering the superconductor and therefore a higher Andreev reflection amplitude.
This provides another mechanism of the gap enhancement.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for different geometries.
With (a) a straight system, (b) a zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for the straight system is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for the zigzag systems.
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are listed at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
\end{figure}

@@

\comment{In a straight system, the Majoranas are very poorly localized because of small gap and high velocity}
We show the resulting Majorana wave function densities $\left| \psi_\textrm{M} \right|^2$ in different geometries in Fig.~\ref{fig:wave_functions} using the same Hamiltonian parameter values.
In the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
This is a result of the small topological gap combined with the quasiparticle velocity $v \approx v_\textrm{F}$ yielding a large Majorana size
\begin{equation}
\label{eq:xi_M}
\xi_\textrm{M}=\hbar \frac{v}{E_\textrm{gap}}.
\end{equation}
This result follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
Therefore, in straight junctions the wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
We observe that in zigzag systems the Majorana properties improve independent of specific geometric details.
All of the zigzag-type geometries have $\xi_\textrm{M}$ improved by a factor $\sim 70$ and have the Majorana wave function localized within one segment of the zigzag.
Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher than in the straight junction, and as mentioned in section \ref{sec:band_structures}, the quasiparticle velocity $v$ is more than an order of magnitude lower.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/phasediagrams}
\caption{A comparison of a straight device (left panels) and a zigzag one (right panels).
The top panels show the Majorana wave functions, near the left edge of the system, at the value of $B_x$ for which $E_\textrm{gap}$ is maximized in a straight geometry for $\mu=\SI{10}{\meV}$ and $\phi=\pi$ as well as the values of the gap and the Majorana size.
The other panels show gap as a function of $\mu$ and $B_x$ at $\phi=\pi$ (middle panels) and as a function of $\phi$ and $B_x$ at $\mu=\SI{10}{\meV}$ (bottom panels).
The dashed lines and the dot indicate the parameters used in the other panels.
Additionally, in subplot (c) we overlay the phase boundaries.
The remaining parameter values are listed at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
\label{fig:phasediagrams}}
\end{figure}

@@

\comment{The zigzag geometry is a controllable tool in hardening the gap and decreasing Majorana size.}
The zigzag geometry increases the topological gap in the high-density regime by more than an order of magnitude, and substantially reduces Majorana size.
The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high-density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
Additionally, it offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, which has a similar effect.

\comment{Zigzag doesn't do anything against other mechanisms, and therefore it doesn't help to use it ignorantly}
A soft gap may arise due to mechanisms that do not involve ballistic trajectories: both interface disorder and pair-breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
Further, in a multimode junction, the dependence of transmission~\cite{Stanescu2014} may produce a subgap conductance similar to that in a device with a soft gap.
The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool to distinguish different mechanisms.

\comment{Optimizing the geometry, more detailed modeling, and a simple analytical estimation are open questions for further research}
Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a possible research avenue of finding the optimal geometry.
A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices.
Finally, we neglected several important physical effects, such as disorder, electrostatics, the orbital effect of the magnetic field, and the finite thickness of the sample.
Although we do not expect these phenomena influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.

\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
The zigzag geometry is within reach of the standard fabrication techniques as demonstrated by an ongoing experimental project~\cite{Vries}.
Further, according to our simulations, the zigzag devices should be robust against the unavoidable variation in the experimental device geometry.
We therefore expect, that the new approach to controlling the proximity superconductivity by means of modifying the geometry will become a commonly used technique.

@@

\section{Interface transparency vs.~path length cut-off}

The zigzag geometry both increases the interface transparency (because particles typically hit the superconductor
closer to normal incidence) as well as sets an upper limit to the trajectory length.
The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm}$ comparable to the Fermi wavelength $\lambda_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.
